---
output:
  pdf_document: default
  html_document: default
  always_allow_html: true
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE,out.extra='trim={0 1cm 0 1cm}') 
```

```{r, message=F, warning=F}
# uploading the libraries 
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(tibble)
library(plotly)
library(gridExtra)
library(scales)
library(crayon)
webshot::install_phantomjs()
```

### **Introduction**
Netflix has grown to be one of the top source of entertainment. The platform has recorded increase of 23 percent in paid memberships during the final quarters of 2019. The projects goal's was to see growth of the Netflix streaming library since 2008 up to early of 2021.

### **Data**
The data set was given by kaggle and can be retrieved from: https://www.kaggle.com/shivamb/netflix-shows

```{r}
# loads that data set
data<- read.csv("Eideted Netlfix sheet.csv")
```

## **Summary of the Data Set**
The overall data set has 11 variables/columns and 7787 objects/rows.

```{r}
# shows first 5 rows of the data set 
head(data)
```

```{r}
# outputs the structure of thee data set
str(data)
# outputs the summary of the data set
summary(data)
```

## **Data Clean-up**
Overall Data Clean-up for the Data set:
1) Changed the format of the date_added column
2) Turned all the blank values into NA's
3) Used a function to get the mode of country, rating and date added. Used the mode values to replace the values that were NA's
4)Dropped columns director and cast
5)Categorized the rating to an age group


```{r}
# filled all blank values with NA
data_new2 <- data                                    
data_new2[data_new2 == "" | data_new2 == " "] <- NA  
head(data_new2)
```

```{r}
# changes format of the date_added 
data_new2$date_added <- mdy(data_new2$date_added)
```

```{r}
# shows the number of NA's values in each columns
colSums(is.na(data_new2))
```


```{r}
# gets mode for rating. data_added, and country and replaces NA's with the mode
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v,uniqv)))]
}
rating_mode<-getmode(data_new2$rating)
data_added_mode <- getmode(data_new2$date_added)
country_mode <-getmode(data_new2$country)

data_new2$rating[which(is.na(data_new2$rating))] <- rating_mode

data_new2$date_added[which(is.na(data_new2$date_added))]<- data_added_mode

data_new2$country[which(is.na(data_new2$country))] <- country_mode
```

```{r}
# drops rows director and cast columns
data_new2 <- data_new2 %>% subset(select=-c(director,cast))
```

```{r}
# shows total of NA's in each columns
colSums(is.na(data_new2))
```

```{r}
# categorizes the rating to an age group
data_new2<-data_new2 %>% mutate(target_age=case_when(rating == 'TV-PG' ~ 'Older Kids', rating=='TV-MA' ~ 'Adults', rating == 'TV-Y7-FV' ~ 'Older Kids', rating == 'TV-Y7' ~ 'Older Kids', rating == 'TV-14' ~ 'Teens', rating == 'R' ~ 'Adults', rating == 'TV-Y'~ 'Kids', rating == 'NR'~ 'Adults', rating == 'PG-13' ~ 'Teens', rating=='TV-G' ~'Kids', rating == 'PG'~ 'Older Kids', rating == 'G'~'Kids', rating == 'UR'~ 'Adults', rating == 'NC-17'~ 'Adults'))
```

## **Percentage of TV and Movie in Netflix**
Here the next following code chunks are to make the visualization for "Percentage of TV and Movie in Netflix". We start with creating a two new data frame one for Movie and TV.
```{r}
# creates new data frame for Movie and TV
movie_df<- data_new2 %>% filter(type=='Movie')
head(movie_df)

tv_df<- data_new2 %>% filter(type=='TV Show')
head(tv_df)
```

Using the new table I then added the total count of Movie and TV. Along with the total percentage of Movie and TV

```{r}
# gets the total percentage and total count of Movies and Tv's
type_df <- data_new2 %>% group_by(type) %>% summarize(counts=n(),percentage=n()/nrow(data_new2))
type_df


```

With type_df created I then added information to a pie chart called type_df_pie. Here we can see Movie is 69% of Netflix's streaming library while TV is 31%

```{r}
# outputs a pie charts of the the total percentage and total count of Movies and Tv's
type_df_pie <- type_df %>% ggplot(aes(x="", y=percentage,fill=type))+ 
  geom_col(type="black")+ 
  coord_polar("y",start=0)+ 
  geom_text(aes(label=paste0(round(percentage*100),"%")),position = position_stack(vjust = 0.5))+ theme(panel.background = element_blank(), axis.line = element_blank(),axis.text = element_blank(), axis.ticks = element_blank(),axis.title = element_blank(),plot.title = element_text(hjust = 0.5,size = 18))+ ggtitle("Percentage of TV and Movie in Netflix")

type_df_pie
```

### **Amount of Netflix Content By Top 10 Countries**
This visualization goes over the number Netflix content for the Top 10 Countries. We see from the visualization that many of the other countries have around the same amount of content, while the United States is the outlier with the most amount of content.
```{r}
k<-strsplit(data_new2$country,split = ",") # splits values country columns

# creates a data frame 
netds_countries<- data.frame(type = rep(data_new2$type, sapply(k, length)), country = unlist(k))
head(netds_countries) 

netds_countries$country<- as.character(netds_countries$country) # converts country as character

 # gets the total count type value for each country
amount_by_country <- netds_countries %>% group_by(country,type)%>% summarise(count=n())

#creates a data frame 
u <- reshape(data=data.frame(amount_by_country),idvar="country",  
                          v.names = "count",
                          timevar = "type",
                          direction="wide") %>% arrange(desc(count.Movie)) %>%
                          top_n(10)

# changes column names
names(u)[2] <- "Number_of_Movies" 
names(u)[3] <- "Number_of_TV_Shows"

u <- u[order(desc(u$Number_of_Movies +u$Number_of_TV_Shows)),]# orders the values in descending order

# outputs the geom_point graph
figure000 <- ggplot(u, aes(Number_of_Movies, Number_of_TV_Shows, colour=country))+  
  geom_point(size=5,alpha=0.5)+
  xlab("Number of Movies") + ylab("Number of TV Shows")+
  ggtitle("Amount of Netflix Content By Top 10 Country")
figure000 # outputs visualization
```

### **Amount of Netflix Content By Time** 
The visualization goes over the amount of Netflix content by time. We can see there was peak in both TV and Movie around 2019 but there was decrease during 2020.
```{r,out.height="170%",out.width="200%"}
f <- data_new2$title # converts the title columns into tibble format
f <-tibble(f)
data_new2$title <- f

# extracts the year from data_added column 
data_new2$new_date <- year(data_new2$date_added)

# creates a new data frame  with type and new_date
df_by_date <- data_new2$title %>% 
  group_by(data_new2$new_date, data_new2$type) %>% 
  na.omit(data_new2$new_date) %>% 
  summarise(added_content_num = n())

head(df_by_date)

# type,new_date and added_content_num into variables 
Type<- df_by_date$`data_new2$type`
Date <- df_by_date$`data_new2$new_date`
Content_Number <- df_by_date$added_content_num
par(mfrow= c(1,2))
# visualization of "Amount of Netflix Content By Time" 
g1<- ggplot(df_by_date, aes(Date, Content_Number))+
  geom_line(aes(colour = Type),size=2)+ 
  geom_point() + 
  xlab("Date") + 
  ylab("Number of Content")+
  ggtitle("Amount of Netflix Content By Time")

ggplotly(g1, dynamicTicks = T)
```

### **Amount of Content By Rating (Movie vs. TV Show)**
The next visualization goes more in depth with the a stacked bar chart to separate the amount of content by rating for Movie vs. TV Show.
```{r,out.height="170%", out.width="200%"}
# group_by's rating and type with the total count
data2<- data_new2$title %>% group_by(data_new2$rating,data_new2$type) %>% summarise(content_num=n())

#renames columns to rating. type, and content
names(data2) [1] <- "rating"
names(data2) [2] <- "type"
names(data2) [3] <- "content"

head(data2)

# create new data frame
newdata2 <- reshape(data=data.frame(data2),idvar="rating",
                          v.names = "content",
                          timevar = "type",
                          direction="wide")

# changes columns names and and if NA prints 0
names(newdata2)[2] <- "Movie"
names(newdata2)[3] <- "TV Show"
newdata2$`TV Show`[is.na(newdata2$`TV Show`)] <- print(0)


# puts rating, Movie, and TV show into variables 
rating <- newdata2$rating
Movie <- newdata2$Movie
Tv_Show <- newdata2$`TV Show`

# visualization for Amount of Content By Rating (Movie vs. TV Show)
figure3 <- plot_ly(newdata2, x = ~rating, y = ~Movie, type = 'bar', name = 'Movie') 
figure3 <- figure3 %>% add_trace(y = ~Tv_Show, name = 'TV Show')
figure3 <- figure3 %>% layout(yaxis = list(title = 'Count'),
                        barmode = 'stack', 
                        title=("Amount of Content By Rating (Movie vs. TV Show)"))


figure3
```

### **Top 20 Genres On Netflix**
The visualization show the top 20 genres on Netflix. When see the genres on the bar graph we can see the international movie as the most amount of content of Netflix. 
```{r}
# converts listed_in to character
data_new2$listed_in<- as.character(data_new2$listed_in)

# splits listed_in values 
t20 <- strsplit(data_new2$listed_in, split = ", ") 

# creates data frame and converts to character
count_list_in <- data.frame(type=rep(data_new2$type,sapply(t20,length)),listed_in=unlist(t20))
count_list_in$listed_in <- as.character(gsub(",","",count_list_in$listed_in))

# gets total count of each listed_in values
df_count_listed_in <- count_list_in %>% 
                            group_by(listed_in) %>% 
                            summarise(count = n()) %>% 
                            top_n(20)
head(df_count_listed_in)


# Visualization of "20 Top Genres On Netflix"
figure5 <- df_count_listed_in %>% ggplot(aes(x= listed_in, y= df_count_listed_in$count)) + geom_bar(stat = "identity") +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ labs(title = "20 Top Genres On Netflix", x="Genres",y="Count")+geom_text(aes(label =df_count_listed_in$count ), vjust = 0)
figure5
```



